---
title: "The South China Sea Dispute"
author: "Jack Carter"  
date: "1/9/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr, warn.conflicts = FALSE)
options(dplyr.summarise.inform = FALSE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(ggthemes)
library(naniar)
library(patchwork)
library(rvest)
library(pdftools)
library(patchwork)

# set the working directory
path <- file.path("C:/Users/HUAWEI/Desktop/China-data/The_South_China_Sea_Dispute/data", fsep = .Platform$file.sep)
setwd(path)

military_USD_data <- read_xls("Military_spending.xls", range = "A4:BL268") %>%
  gather(key = "year", value = "military_USD", 35:64) %>%
  rename(country = "Country Name") %>%
  subset(select = -c(2:34))

# group for analysis
countries <- c("China, People's Republic of", "Philippines", "Malaysia", "Taiwan Province of China", "Vietnam")

```

## **Executive Summary**

The South China Sea is of great strategic importance due to its abundance of valuable resources such as oil, natural gas and fish. The largest source of regional wealth however is international trade. Trade security thus appears to be the single most significant motivation to contest this disputed territory.

Power is not equally distributed among the claimants however. China remains by far the largest state involved and, importantly, has the highest military spending. It is for this reason that the smaller states feel overwhelmed and have called upon the US for support.

The US's "Pivot to Asia" policy in 2012 has since bought the region an extra element of geopolitical competition. The US's military spending remains far higher than China's. But if China's economy continues to grow, the US could one day find itself facing an equally matched rival in East Asia. 

The rest of the report analyzes the South China Sea dispute in the context of the resources, claimants and global superpowers involved. It is organized into the following sections:

1. The Region
2. The Claimants  
3. Superpower Competition  
4. Conclusion
5. Sources

&nbsp;

## **1. The Region**

### **1.1: Resources**  
Expressed as an estimate value of the region's total oil reserves, total natural gas reserves, annual fish stock and annual maritime trade in US Dollars *(CSIS, 2016; CSIS, 2021; Teh et.al., 2019)*.

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

# resources plot
oil <- 605.44
oil <- tibble(oil)
gas <- 995.6
gas <- tibble(gas)
fish <- 584.90
fish <- tibble(fish)
trade <- 3400
trade <- tibble(trade)

tidy_resources_value <- oil %>%
  cbind(gas) %>%
  cbind(fish) %>%
  cbind(trade) %>%
  gather(key = measure, value = value)

tidy_resources_value %>%
  mutate(measure = as.factor(measure), measure = factor(measure, levels = c("oil", "gas", "fish", "trade"))) %>%
  ggplot(aes(x = measure, y = value/10^3, fill = measure)) +
  geom_bar(stat = "identity", position="dodge", alpha = 0.9, show.legend = T) +
  ggtitle("Resources") +
  xlab("") +
  ylab("USD (Trillions)") +
  scale_x_discrete(labels = c("Oil", "Gas", "Fish", "Trade")) +
  scale_fill_manual(values = c("#D55E00", "#E6AB02", "#7570B3", "#1B9E77"), labels = c("Oil", "Natural Gas", "Fish", "Trade")) +
  theme_economist_white(gray_bg = FALSE) +
  theme(plot.title = element_text(hjust = 0.5, size = 10, color = "#474747"),
        plot.margin = unit(c(0.75, 0.75, 0.75, 0.75), "cm"),
        axis.text = element_text(size = 9, color = "gray30"),
        axis.text.x=element_text(vjust = -5),
        axis.title.x = element_text(size = 9, color = "gray30", vjust = -8),
        axis.title.y = element_text(size = 9, color = "gray30", vjust = 2.5),
        legend.direction = "vertical", 
        legend.position = "right",
        legend.title = element_blank(),
        legend.text = element_text(size = 12, color = "gray20"),
        legend.spacing.x = unit(0.25, "cm"),
        legend.key.size = unit(1, "cm"), 
        legend.key.height = unit(0.75, "cm"))

```

The data shows that while oil, natural gas and fish are important, trade appears to be the most significant source of regional wealth. This suggests that control over the waterway is primarily sought after due to its ability to safeguard access to global markets.

&nbsp;

### **1.2: Global Trade Routes**  
Expressed as total trade in trillions of US Dollars for selected global shipping lanes *(CSIS, 2016; IFC., 2016; Osler, 2019; Kenawy, 2015)*.

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

# trade routes plot
routes <- tibble(routes = c("Hormuz", "Panama", "SCS", "Suez"))
trade <- tibble(trade = c(554, 270, 3400, 1692))
tidy_trade_routes <- routes %>%
  cbind(trade) %>%
  mutate(description = c("$0.55 Trillion", "$0.27 Trillion", "$3.4 Trillion", "$1.7 Trillion"))

tidy_trade_routes %>%
  mutate(routes = as.factor(routes), routes = factor(routes, levels = c("Hormuz", "Panama", "SCS", "Suez"))) %>%
  ggplot(aes(x = routes, y = trade/10^3, col = routes, size = trade)) +
  geom_point(alpha = 0.9) +
  geom_text(aes(label=description),hjust="center", vjust="center", size=c(1.75, 1, 3.25, 2.5), colour="#FFFAF0") +
  scale_size_area(max_size = 38, guide = 'none') +
  guides(colour = guide_legend(override.aes = list(size=7.5))) +
  ggtitle("Global Trade Routes") +
  xlab("") +
  ylab("USD (Trillions)") +
  ylim(0, 4) +
  scale_x_discrete(labels = c("Middle East", "Americas", "East Asia", "North Africa")) +
  scale_color_manual(values = c("#D55E00", "#E6AB02", "#7570B3", "#1B9E77"), labels = c("Strait of Hormuz", "Panama Canal", "South China Sea", "Suez Canal")) +
  theme_economist_white(gray_bg = FALSE) +
  theme(plot.title = element_text(hjust = 0.5, vjust = 0.75, size = 10, color = "#474747"),
        plot.margin = unit(c(0.75, 0.75, 0.75, 0.75), "cm"),
        axis.text = element_text(size = 9, color = "gray30"),
        axis.text.x=element_text(vjust = -4),
        axis.title.x = element_text(size = 9, color = "gray30", vjust = -8),
        axis.title.y = element_text(size = 9, color = "gray30", vjust = 2.5),
        legend.direction = "vertical", 
        legend.position = "right",
        legend.title = element_blank(),
        legend.text = element_text(size = 12, color = "gray20"),
        legend.spacing.x = unit(0.25, "cm"),
        legend.key.size = unit(1, "cm"), 
        legend.key.height = unit(0.75, "cm"))

```

The data shows that the South China Sea is significant global shipping lane for total trade respectively. 

&nbsp;

### **1.3: Claimants' Regional Trade**  
Expressed as the import value, export value and percentage of the total trade for parties to the dispute passing through the South China Sea in 2016 *(CSIS, 2016)*.

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

# trade value plot
country <- tibble(country = c("China, People's Republic of", "Malaysia", "Philippines", "Taiwan Province of China", "Vietnam"))
exports <- tibble(exports = c(874, 106, 31, 97, 158))
imports <- tibble(imports = c(598, 106, 75, 108, 161))
total <- tibble(total = c(39, 58, 72, 40, 86))
tidy_trade_value <- country %>%
  cbind(exports) %>%
  cbind(imports) %>%
  cbind(total) %>%
  gather(key = measure, value = value, -1)

tidy_trade_value %>%
  mutate(measure = as.factor(measure), measure = factor(measure, levels = c("imports", "exports", "total"))) %>%
  ggplot(aes(x = measure, y = value, fill = country)) +
  geom_bar(alpha = 0.9, stat='identity', position="fill", show.legend = TRUE) +
  ggtitle("Claimants' Regional Trade") +
  xlab("") +
  ylab("Relative Share (%)") +
  scale_x_discrete(labels = c("Import Value", "Export Value", "Share of State's Total")) +
  scale_fill_manual(values = c("#D55E00", "#E6AB02", "#7570B3", "#1B9E77", "#E7298A"), labels = c("China", "Malaysia", "Philippines", "Taiwan", "Vietnam")) +
  theme_economist_white(gray_bg = FALSE) +
  theme(plot.title = element_text(hjust = 0.5, size = 10, color = "#474747"),
        plot.margin = unit(c(0.75, 0.75, 0.75, 0.75), "cm"),
        axis.text = element_text(size = 9, color = "gray30"),
        axis.text.x=element_text(vjust = -4),
        axis.title.x = element_text(size = 9, color = "gray30", vjust = -8),
        axis.title.y = element_text(size = 9, color = "gray30", vjust = 2.5),
        legend.direction = "vertical", 
        legend.position = "right",
        legend.title = element_blank(),
        legend.text = element_text(size = 12, color = "gray20"),
        legend.spacing.x = unit(0.25, "cm"),
        legend.key.size = unit(1, "cm"), 
        legend.key.height = unit(0.75, "cm"))

```

The data shows that China's regional trade is far higher than that of the other claimants. This suggests that it potentially has more to lose if this global sea lane faces disruptions. 

&nbsp;

## **2. The Claimants**

### **2.1: Regional Influence**  
Expressed as total land, population and gross domestic product (GDP) in 2021 *(Global Firepower, 2021)*. 

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

# lopsided size plot
Land <- tibble(Land = c(9596961, 329847, 300000, 35980, 331210))
  Land <- tibble(Land / sum(Land))
Population <- tibble(Population = c(1394015977, 32652083, 109180815, 23603049, 98721275))
  Population <- tibble(Population / sum(Population))
GDP <- tibble(GDP = c(25400000000000, 977500000000, 931000000000, 1213500000000, 686500000000))
  GDP <- tibble(GDP / sum(GDP))
Military <- tibble("Military Spending" = c(178200000000, 3850000000, 4250000000, 13000000000, 6390000000))
  Military <- tibble(Military / sum(Military))

country <- tibble(c("China, People's Republic of", "Malaysia", "Philippines", "Taiwan Province of China", "Vietnam")) %>% rename(country = `c(...)`)
tidy_size <- country %>%
    cbind(Land) %>%
    cbind(Population) %>%
    cbind(GDP) %>%
    cbind(Military) %>%
    gather(key = measure, value = value, -1)

tidy_size %>%
  mutate(measure = as.factor(measure), measure = factor(measure, levels = c("Land", "Population", "GDP", "Military Spending"))) %>%
  ggplot(aes(x = country, y = value, fill = country)) +
  geom_bar(alpha = 0.9, stat = "identity", position = "dodge") +
  facet_wrap(~ measure) +
  ggtitle("") +
  xlab("") +
  ylab("Relative Share (%)") +
  scale_fill_manual(values = c("#D55E00", "#E6AB02", "#7570B3", "#1B9E77", "#E7298A"), labels = c("China", "Malaysia", "Philippines", "Taiwan", "Vietnam")) +
  theme_economist_white(gray_bg = FALSE) +
  theme(plot.title = element_text(hjust = 0.5, size = 10, color = "#474747"),
        plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"),
        strip.text = element_text(hjust = 0.5, vjust = 1.075, size = 10, color = "#474747"),
        panel.spacing = unit(1.5, "lines"),
        axis.text = element_text(size = 9, color = "gray30"),
        axis.text.x = element_blank(),
        axis.title.x = element_text(size = 9, color = "gray30", vjust = -8),
        axis.title.y = element_text(size = 9, color = "gray30", vjust = 2.5),
        legend.direction = "vertical", 
        legend.position = "right",
        legend.title = element_blank(),
        legend.text = element_text(size = 12, color = "gray20"),
        legend.spacing.x = unit(0.25, "cm"),
        legend.key.size = unit(1, "cm"), 
        legend.key.height = unit(0.75, "cm"))

```

The data shows a significantly larger landmass, population and GDP for China. This suggests that the country likely has far greater coercive abilities vis a vis its smaller neighbors.

&nbsp;

### **2.2: Military Spending**  
Expressed as military spending between 1990 and 2019 *(World Bank, 2019)*. 

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

# military spending plot
military_USD_data %>%
  mutate(year = as.numeric(year)) %>%
  mutate(country = factor(country, levels = c("China, People's Republic of", "Malaysia", "Philippines", "Taiwan Province of China", "Vietnam"))) %>%
  filter(country %in% countries[-4], !is.na(military_USD)) %>%
  ggplot(aes(x = year, military_USD / 10^9, fill = country)) +
  geom_area(aes(x = year, y = military_USD / 10^9), alpha = 0.9, stat = "identity", position = "fill") +
  ggtitle("Military Spending") +
  ylab("Relative Share (%)") +
  xlab("") +          
  scale_fill_manual(values = c("#D55E00", "#E6AB02", "#7570B3", "#E7298A"), labels = c("China", "Malaysia", "Philippines", "Vietnam")) +
  theme_economist_white(gray_bg = FALSE) +
  theme(plot.title = element_text(hjust = 0.5, size = 10, color = "#474747"),
        plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"),
        strip.text = element_text(hjust = 0.5, vjust = 1.075, size = 10, color = "#474747"),
        panel.spacing = unit(1.5, "lines"),
        axis.text = element_text(size = 9, color = "gray30"),
        axis.title.x = element_text(size = 9, color = "gray30", vjust = -8),
        axis.title.y = element_text(size = 9, color = "gray30", vjust = 2.5),
        axis.text.y = element_blank(),
        legend.direction = "vertical", 
        legend.position = "right",
        legend.title = element_blank(),
        legend.text = element_text(size = 12, color = "gray20"),
        legend.spacing.x = unit(0.25, "cm"),
        legend.key.size = unit(1, "cm"), 
        legend.key.height = unit(0.75, "cm"))

```

The data shows that China's military spending has far outpaced the others, especially from 2000 to 2020. This suggests that China has a far more capable military than its smaller neighbors.  

&nbsp;

### **2.3: Military Capabilities**  
Expressed as military personnel, aircraft fleet and navy fleet in 2021 *(Global Firepower, 2021)*. 

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

# military power plot
spending <- tibble(spending = c(178.2, 3.85, 4.25, 13, 6.39))
personnel <- tibble(personnel = c(2.185, 0.11, 0.125, 0.165, 0.4825))
aircraft <- tibble(aircraft = c(3260, 147, 179, 739, 247))
navy <- tibble(navy = c(777, 61, 103, 117, 65))
submarines <- tibble(submarines = c(79, 2, 0, 4, 6))

country <- tibble(c("China, People's Republic of", "Malaysia", "Philippines", "Taiwan Province of China", "Vietnam")) %>% rename(country = `c(...)`)
tidy_military <- country %>%
  cbind(personnel) %>%
  cbind(aircraft) %>%
  cbind(navy) %>%
  gather(key = measure, value = value, -1)

tidy_military %>%
  mutate(measure = as.factor(measure), measure = factor(measure, levels = c("personnel", "aircraft", "navy"))) %>%
  mutate(country = factor(country, levels = c("China, People's Republic of", "Malaysia", "Philippines", "Taiwan Province of China", "Vietnam"))) %>%
  ggplot(aes(x = measure, y = value, fill = country)) +
  geom_bar(alpha = 0.9, stat='identity', position="fill", show.legend = TRUE) +
  ggtitle("Military Capabilities") +
  xlab("") +
  ylab("Relative Share (%)") +
  scale_x_discrete(labels = c("Armed Forces", "Aircraft", "Navy")) +
  scale_fill_manual(values = c("#D55E00", "#E6AB02", "#7570B3", "#1B9E77", "#E7298A"), labels = c("China", "Malaysia", "Philippines", "Taiwan", "Vietnam")) +
  theme_economist_white(gray_bg = FALSE) +
  theme(plot.title = element_text(hjust = 0.5, size = 10, color = "#474747"),
        plot.margin = unit(c(0.75, 0.75, 0.75, 0.75), "cm"),
        axis.text = element_text(size = 9, color = "gray30"),
        axis.text.x=element_text(vjust = -4),
        axis.title.x = element_text(size = 9, color = "gray30", vjust = -8),
        axis.title.y = element_text(size = 9, color = "gray30", vjust = 2.5),
        legend.direction = "vertical", 
        legend.position = "right",
        legend.title = element_blank(),
        legend.text = element_text(size = 12, color = "gray20"),
        legend.spacing.x = unit(0.25, "cm"),
        legend.key.size = unit(1, "cm"), 
        legend.key.height = unit(0.75, "cm"))

```

The data shows far greater military capabilities for China. It also shows how China's most overwhelming capability compared to the others is its navy, suggesting that it may have prioritized this arm of the military in response to the ongoing dispute. 

&nbsp;

## **3. Superpower Competition**

### **3.1: Global Influence**  
Expressed as total land, population and gross domestic product (GDP) in 2021 *(Global Firepower, 2021)*. 

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

# lopsided size plot
Land <- tibble(Land = c(9596961, 9826675))
  Land <- tibble(Land / sum(Land))
Population <- tibble(Population = c(1394015977, 332639102))
  Population <- tibble(Population / sum(Population))
GDP <- tibble(GDP = c(25400000000000, 19500000000000))
  GDP <- tibble(GDP / sum(GDP))
Military <- tibble("Military Spending" = c(178200000000, 740500000000))
  Military <- tibble(Military / sum(Military))

country <- tibble(country = c("China, People's Republic of", "The US"))
tidy_size <- country %>%
    cbind(Land) %>%
    cbind(Population) %>%
    cbind(GDP) %>%
    cbind(Military) %>%
    gather(key = measure, value = value, -1)

tidy_size %>%
  mutate(measure = as.factor(measure), measure = factor(measure, levels = c("Land", "Population", "GDP", "Military Spending"))) %>%
  ggplot(aes(x = country, y = value, fill = country)) +
  geom_bar(alpha = 0.9, stat = "identity", position = "dodge") +
  facet_wrap(~ measure) +
  ggtitle("") +
  xlab("") +
  ylab("Relative Share (%)") +
  scale_fill_manual(values = c("#D55E00", "#0072B2"), labels = c("China", "US")) +
  theme_economist_white(gray_bg = FALSE) +
  theme(plot.title = element_text(hjust = 0.5, size = 10, color = "#474747"),
        plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"),
        strip.text = element_text(hjust = 0.5, vjust = 1.075, size = 10, color = "#474747"),
        panel.spacing = unit(1.5, "lines"),
        axis.text = element_text(size = 9, color = "gray30"),
        axis.text.x = element_blank(),
        axis.title.x = element_text(size = 9, color = "gray30", vjust = -8),
        axis.title.y = element_text(size = 9, color = "gray30", vjust = 2.5),
        legend.direction = "vertical", 
        legend.position = "right",
        legend.title = element_blank(),
        legend.text = element_text(size = 12, color = "gray20"),
        legend.spacing.x = unit(0.25, "cm"),
        legend.key.size = unit(1, "cm"), 
        legend.key.height = unit(0.75, "cm"))

```

The data shows that although China has a far larger population, the US still has by far the largest military spedning. This suggests that China is still a rising power and may one day become more powerfull than the US. 

&nbsp;

### **3.2: Military Spending**  
Expressed as military spending between 1990 and 2019 *(World Bank, 2019)*.

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}


# military spending plot
military_USD_data %>%
  mutate(year = as.numeric(year)) %>%
  mutate(country = factor(country, levels = c("China, People's Republic of", "United States"))) %>%
  filter(country %in% c("China, People's Republic of", "United States"), !is.na(military_USD)) %>%
  ggplot(aes(x = year, military_USD / 10^9, fill = country)) +
  geom_area(aes(x = year, y = military_USD / 10^9), alpha = 0.9, position = "fill") +
  ggtitle("Military Spending") +
  xlab("") +          
  ylab("Relative Share (%)") +
  scale_fill_manual(values = c("#D55E00", "#0072B2"), labels = c("China", "US")) +
  theme_economist_white(gray_bg = FALSE) +
  theme(plot.title = element_text(hjust = 0.5, size = 10, color = "#474747"),
        plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), "cm"),
        strip.text = element_text(hjust = 0.5, vjust = 1.075, size = 10, color = "#474747"),
        panel.spacing = unit(1.5, "lines"),
        axis.text = element_text(size = 9, color = "gray30"),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 9, color = "gray30", vjust = -8),
        axis.title.y = element_text(size = 9, color = "gray30", vjust = 2.5),
        legend.direction = "vertical", 
        legend.position = "right",
        legend.text = element_text(size = 12, color = "gray20"),
        legend.spacing.x = unit(0.25, "cm"),
        legend.key.size = unit(1, "cm"), 
        legend.key.height = unit(0.75, "cm"))

```

The data shows that since the year 2000, China's military spending has increased rapidly. This suggests that if its economy continues to grow, it may one day be able to rival the military spending of the US. 

&nbsp;

### **3.3: Military Capabilities**  
Expressed as military personnel, aircraft fleet and navy fleet in 2021 *(Global Firepower, 2021)*. 

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

# military power plot
spending <- tibble(spending = c(178.2, 74.05))
personnel <- tibble(personnel = c(2.185, 1.4))
aircraft <- tibble(aircraft = c(3260, 13233))
navy <- tibble(navy = c(777, 490))
submarines <- tibble(submarines = c(79, 68))

country <- tibble(country = c("China, People's Republic of", "The US"))
tidy_military <- country %>%
  cbind(personnel) %>%
  cbind(aircraft) %>%
  cbind(navy) %>%
  gather(key = measure, value = value, -1)

tidy_military %>%
  mutate(measure = as.factor(measure), measure = factor(measure, levels = c("personnel", "aircraft", "navy"))) %>%
  mutate(country = factor(country, levels = c("China, People's Republic of", "The US"))) %>%
  ggplot(aes(x = measure, y = value, fill = country)) +
  geom_bar(alpha = 0.9, stat='identity', position="fill", show.legend = TRUE) +
  ggtitle("Military Capabilities") +
  xlab("") +
  ylab("Relative Share (%)") +
  scale_x_discrete(labels = c("Armed Forces", "Aircraft", "Navy")) +
  scale_fill_manual(values = c("#D55E00", "#0072B2"), labels = c("China", "US")) +
  theme_economist_white(gray_bg = FALSE) +
  theme(plot.title = element_text(hjust = 0.5, size = 10, color = "#474747"),
        plot.margin = unit(c(0.75, 0.75, 0.75, 0.75), "cm"),
        axis.text = element_text(size = 9, color = "gray30"),
        axis.text.x=element_text(vjust = -4),
        axis.title.x = element_text(size = 9, color = "gray30", vjust = -8),
        axis.title.y = element_text(size = 9, color = "gray30", vjust = 2.5),
        legend.direction = "vertical", 
        legend.position = "right",
        legend.title = element_blank(),
        legend.text = element_text(size = 12, color = "gray20"),
        legend.spacing.x = unit(0.25, "cm"),
        legend.key.size = unit(1, "cm"), 
        legend.key.height = unit(0.75, "cm"))

```

The data shows that despite having a smaller aircraft fleet, China has a larger armed forces and navy fleet. This suggests that China's relative power in the South China Sea will only grow as it continues to prioritize the development of its navy. 

&nbsp;

## **4. Conclusion**

The South China Sea dispute is complex due to the resources involved. The area is home to an abundant supply of oil, natural gas and fish. These is extremely important resources for nations with growing industrial economies and populations. The most important of source of regional wealth for the claimants however appears to be international trade. 

In their bid to ensure their own trade security however, not all of the nations involved are equally matched. China towers over the other claimants in terms fo raw size and power. Its military capabilities are far superior and could continue to grow exponentially relative to its smaller neighbors if its economy does not crash and burn. 

It if for this reason that many of the smaller claimants have called upon the US to maintain the regional balance of power. Ever since it's Pivot to Asia policy in 2012, this is precisely what this superpower has done. Yet this poses additional security risks by adding another layer of geopolitical competition to the region's fragile security situation.

What will the future hold for a territorial dispute involving great strategic importance, mutually incompatible national claims and a superpower competition? Will the region take the path of greater competition or cooperation? Only time will tell. 

&nbsp;

## **5. Sources**

- CSIS. (2016). How Much Trade Transits the South China Sea?.
https://chinapower.csis.org/.

- CSIS. (2021). Asia Maritime Transparency Initiative. https://amti.csis.org/.

- Global Firepower. (2021). GLOBAL FIREPOWER 2021. https://www.globalfirepower.com/.

- IFC. (2016). Panama Canal Expansion—Key to Global Trade. https://www.ifc.org/.

- Kenawy, E. (2015). The expected economic effects of the new Suez Canal project in Egypt. European Journal of Academic Essays. 12 (1), pp.13-22.

- Osler, D. (2019). Hormuz blockade would mean $554bn hit to seaborne trade. https://lloydslist.maritimeintelligence.informa.com/.

- Teh, L et.al.. (2019). Status, Trends, and the Future of Fisheries in the East and South China Seas. Fisheries Centre Research Reports. 27 (1), pp.0-101.

- World Bank. (2019). World Bank Open Data. https://data.worldbank.org/.

&nbsp;
&nbsp;
&nbsp;
&nbsp;



