---
title: "The South China Sea"
author: "Jack Carter"  
date: "1/9/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr, warn.conflicts = FALSE)
options(dplyr.summarise.inform = FALSE)
library(tidyverse)
library(readxl)
library(ggplot2)
library(ggthemes)
library(naniar)
library(patchwork)
library(rvest)
library(pdftools)
library(patchwork)

# set the working directory
path <- file.path("C:/Users/HUAWEI/Desktop/China-data/The_South_China_Sea/data", fsep = .Platform$file.sep)
setwd(path)

# functions
get_world_bank_data <- function(link, col_name) {
  data <- read_xls(link, range = "A4:BL268") %>%
    gather(key = "year", value = col_name, 35:64) %>%
    dplyr::rename(country = `Country Name`) %>%
    subset(select = -c(2:34))
  return(data)
}

# military spending data
military_USD_data <- get_world_bank_data("Military_spending.xls") %>%
  dplyr::rename("military_USD" = col_name)

# my theme
my_personal_theme <- theme(plot.title = element_text(hjust = 0.5, 
                                                     vjust = 7.5, 
                                                     size = 12, 
                                                     color = "#474747"),
                           plot.margin = unit(c(1.5, 1, 1.5, 1), "cm"),
                           axis.text = element_text(size = 9, 
                                                    color = "gray30"),
                           axis.text.x=element_text(vjust = -2.5),
                           axis.title.x = element_text(size = 9, 
                                                       color = "gray30", 
                                                       vjust = -10),
                           axis.title.y = element_text(size = 9, 
                                                       color = "gray30", 
                                                       vjust = 10),
                           legend.direction = "vertical", 
                           legend.position = "right",
                           legend.title = element_blank(),
                           legend.text = element_text(size = 12, 
                                                      color = "gray20"),
                           legend.margin=margin(1, -15, 1, 0),
                           legend.spacing.x = unit(0.25, "cm"),
                           legend.key.size = unit(1, "cm"), 
                           legend.key.height = unit(0.75, "cm"),
                           strip.text = element_text(hjust = 0.5, 
                                                     vjust = 1, 
                                                     size = 10, 
                                                     color = "#474747"),
                           panel.spacing = unit(2, "lines"))

# group for analysis
countries <- c("China, People's Republic of", "Philippines", "Malaysia", "Taiwan Province of China", "Vietnam")

```

## **Executive Summary**

The South China Sea is a region of great strategic importance. This appears to have led in recent decades to a series of increasingly contested  maritime claims between China, Malaysia, the Philippines, Taiwan and Vietnam. China's dominance has prompted the US to step in to maintain the regional balance of power. Yet the US's current military advantage could be short lived if China's economy continues to grow. 

The rest of the report analyzes the dispute in the context of the region's strategic importance, China's dominance over the other claimants and the China-US balance of power. It is organized into the following sections:

1. The Region
2. The Claimants  
3. The Superpowers

&nbsp;

## **1. The Region**

1.1: The approximate value of regional revenue sources *(CSIS, 2016: CSIS, 2021: Teh et.al., 2019)*.

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

resource_value <- tibble(resource = c("3. Fish", "4. Trade", 
                                      "1. Oil", "2. Gas"),
                         value = c(584.90, 3400, 605.44, 995.6),
                         label = c("$0.58 Trillion", "$3.4 Trillion",
                                   "$0.6 Trillion", "$1 Trillion"))

resource_value %>%
  ggplot(aes(x = resource, y = value/10^3, col = resource, size = value)) +
  geom_point(alpha = 0.9) +
  geom_text(aes(label=label),hjust="center", vjust="center", size=c(1.5, 3.5, 1.5, 2.5), colour="#FFFAF0") +
  scale_size_area(max_size = 38, guide = 'none') +
  guides(colour = guide_legend(override.aes = list(size=7.5))) +
  ggtitle("Strategic Importance") +
  xlab("") +
  ylab("Trillions (USD)") +
  ylim(0, 4.2) +
  scale_color_manual(values = c("#D55E00", "#E6AB02", "#7570B3", "#1B9E77"), 
                     labels = c("Total Oil", "Total Gas",
                                "Annual Fish", "Annual Trade")) +
  theme_economist_white(gray_bg = FALSE) +
  my_personal_theme +
  theme(axis.text.x=element_blank())

```

1.2: The approximate value of trade routes in trillions of US Dollars *(CSIS, 2016: Allianz, 2016: Osler, 2019: Kenawy, 2015)*.

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

trade_routes <- tibble(route = c("Hormuz", "Panama", "SCS", "Suez"),
                       trade = c(554, 270, 3400, 1692),
                       label = c("$0.55 Trillion", "$0.27 Trillion", 
                                 "$3.4 Trillion", "$1.7 Trillion"))

trade_routes %>%
  ggplot(aes(x = route, y = trade/10^3, col = route, size = trade)) +
  geom_point(alpha = 0.9) +
  geom_text(aes(label=label),hjust="center", vjust="center", size=c(1.5, 1, 3.25, 2.5), colour="#FFFAF0") +
  scale_size_area(max_size = 38, guide = 'none') +
  guides(colour = guide_legend(override.aes = list(size=7.5))) +
  ggtitle("Trade Cargo") +
  xlab("") +
  ylab("Trillions (USD)") +
  ylim(0, 4.2) +
  scale_x_discrete(labels = c("Middle East", "Americas", "East Asia", "North Africa")) +
  scale_color_manual(values = c("#D55E00", "#E6AB02", "#7570B3", "#1B9E77"), labels = c("Strait of Hormuz", "Panama Canal", "South China Sea", "Suez Canal")) +
  theme_economist_white(gray_bg = FALSE) +
  my_personal_theme

```

1.3: The approximate volume of oil cargo routes in millions of barrels per day in 2016 *(EIA, 2017)*.

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

oil_routes <- tibble(route = c("Hormuz", "Panama", "SCS", "Suez"),
                     oil = c(18.5, 1, 16, 5.5),
                     label = c("18.5 million", "1 Million", 
                                "16 Million", "5.5 Million"))

oil_routes %>%
  ggplot(aes(x = route, y = oil, col = route, size = oil)) +
  geom_point(alpha = 0.9) +
  geom_text(aes(label=label),hjust="center", vjust="center", size=c(3.75, 1.15, 3.25, 1.75), colour="white") +
  scale_size_area(max_size = 38, guide = 'none') +
  guides(colour = guide_legend(override.aes = list(size=7.5))) +
  ggtitle("Oil Cargo") +
  xlab("") +
  ylab("Millions (BPD)") +
  ylim(0, 25) +
  scale_x_discrete(labels = c("Middle East", "Americas", "East Asia", "North Africa")) +
  scale_color_manual(values = c("#D55E00", "#E6AB02", "#7570B3", "#1B9E77"), labels = c("Strait of Hormuz", "Panama Canal", "South China Sea", "Suez Canal")) +
  theme_economist_white(gray_bg = FALSE) +
  my_personal_theme

```

## **Regional Summary**
The region is characterized by tremendous strategic importance due to its abundance of estimated oil and gas reserves, fish supplies and international trade flows. 

Yet while hydrocarbon reserves and fish supplies may be significant, they are easily overshadowed by the value of international trade. The region is not only home to the world's largest international trade flows, but also the second largest crude oil flows. This makes it a crucial choke point in the global economy and thus a vital national interest.

&nbsp;

## **2. The Claimants**

2.1: Regional influence by total land, population, GDP and exports in 2021 *(Global Firepower, 2021, CSIS, 2016)*. 

```{r echo=FALSE, message=FALSE, warning=FALSE, dpi=600}

regional_influence <- tibble(country = c("China", "Malaysia", "Philippines",
                                         "Taiwan", "Vietnam"),
                             "Land" = c(9596961, 329847, 
                                       300000, 35980, 331210),
                             "Population" = c(1394015977, 32652083, 
                                            109180815, 23603049, 
                                            98721275),
                             "GDP" = c(25400000000000, 977500000000,
                                     931000000000, 1213500000000,
                                     686500000000),
                             "Exports" = c(874, 106, 31, 97, 158)) %>%
  gather(key = measure, value = value, -1) %>%
  group_by(measure) %>%
  mutate(value = value / sum(value))

regional_influence %>%
  mutate(measure = as.factor(measure), measure = factor(measure, levels = c("Land", "Population", "GDP", "Exports"))) %>%
  ggplot(aes(x = country, y = value, fill = country)) +
  geom_bar(alpha = 0.9, stat = "identity", position = "dodge") +
  facet_wrap(~ measure) +
  ggtitle("Regional Influence") +
  xlab("") +
  ylab("Relative Share (%)") +
  scale_fill_manual(values = c("#D55E00", "#E6AB02", "#7570B3", "#1B9E77", "#E7298A"), labels = c("China", "Malaysia", "Philippines", "Taiwan", "Vietnam")) +
  theme_economist_white(gray_bg = FALSE) +
  my_personal_theme +
  theme(axis.text.x=element_blank())

```

2.2: Mlitary spending between 1990 and 2019 *(World Bank, 2019)*. 

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

military_USD_data %>%
  mutate(year = as.numeric(year)) %>%
  mutate(country = factor(country, levels = c("China, People's Republic of", "Malaysia", "Philippines", "Taiwan Province of China", "Vietnam"))) %>%
  filter(country %in% countries[-4], !is.na(military_USD)) %>%
  ggplot(aes(x = year, military_USD / 10^9, fill = country)) +
  geom_area(aes(x = year, y = military_USD / 10^9), alpha = 0.9, stat = "identity", position = "fill") +
  ggtitle("Military Spending") +
  ylab("Relative Share (%)") +
  xlab("") +          
  scale_fill_manual(values = c("#D55E00", "#E6AB02", "#7570B3", "#E7298A"), labels = c("China", "Malaysia", "Philippines", "Vietnam")) +
  theme_economist_white(gray_bg = FALSE) +
  my_personal_theme

```

3.3: Coercive power in 2021 *(Global Firepower, 2021)*. 

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

claimant_military_power <- tibble(country = c("China", "Malaysia", "Philippines",
                                              "Taiwan", "Vietnam"),
                                  aircraft_carriers = c(2, 0, 0, 0, 0),
                                  destroyers = c(50, 0, 0, 4, 0),
                                  submarines = c(79, 2, 0, 4, 6),
                                  fighters = c(1200, 26, 0, 288, 75)) %>%
  gather(key = measure, value = value, -1)  %>%
  group_by(measure) %>%
  mutate(value = value / sum(value))

claimant_military_power %>%
  mutate(measure = factor(measure, levels = c("aircraft_carriers", "destroyers", 
                                              "submarines", "fighters"))) %>%
  ggplot(aes(x = measure, y = value, fill = country)) +
  geom_bar(alpha = 0.9, stat='identity', position="fill", show.legend = TRUE) +
  ggtitle("Coercive Power") +
  xlab("") +
  ylab("Relative Share (%)") +
  scale_x_discrete(labels = c("Aircraft Carriers", "Destroyers", "Submarines", "Fighter Jets")) +
  scale_fill_manual(values = c("#D55E00", "#E6AB02", "#7570B3", "#1B9E77", "#E7298A"), 
                    labels = c("China", "Malaysia", "Philippines", "Taiwan", "Vietnam")) +
  theme_economist_white(gray_bg = FALSE) +
  my_personal_theme

```

## **Claimant Summary**
The claimants are characterized by a high degree of inequality in both size and capabilities. China has by far the largest regional trade flows, landmass, population, GDP and military resources.

This suggests that the dispute is highly one-sided in terms of raw power, an intuition borne out by the fact that China has now militarized more islands than all of the other claimants combined. It is for this reason that the US has stepped up its regional military presence since 2012. 

&nbsp;

## **3. The Superpowers**

3.1: Global influence by total land, population, GDP and exports in 2021 *(Global Firepower, 2021: CSIS, 2016)*. 

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

global_influence <- tibble(country = c("China", "US"),
                            "Land" = c(9596961, 9826675),
                            "Population" = c(1394015977, 332639102),
                            "GDP" = c(25400000000000, 19500000000000),
                            "Exports" = c(874, 83)) %>%
  gather(key = measure, value = value, -1) %>%
  group_by(measure) %>%
  mutate(value = value / sum(value))


global_influence %>%
  mutate(measure = as.factor(measure), measure = factor(measure, levels = c("Land", "Population", "GDP", "Exports"))) %>%
  ggplot(aes(x = country, y = value, fill = country)) +
  geom_bar(alpha = 0.9, stat = "identity", position = "dodge") +
  facet_wrap(~ measure) +
  ggtitle("Global Influence") +
  xlab("") +
  ylab("Relative Share (%)") +
  scale_fill_manual(values = c("#D55E00", "#0072B2"), labels = c("China", "US")) +
  theme_economist_white(gray_bg = FALSE) +
  my_personal_theme

```

3.2: Military spending between 1990 and 2019 *(World Bank, 2019)*. 

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

military_USD_data %>%
  mutate(year = as.numeric(year)) %>%
  mutate(country = factor(country, levels = c("China, People's Republic of", "United States"))) %>%
  filter(country %in% c("China, People's Republic of", "United States"), !is.na(military_USD)) %>%
  ggplot(aes(x = year, military_USD / 10^9, fill = country)) +
  geom_area(aes(x = year, y = military_USD / 10^9), alpha = 0.9, position = "fill") +
  ggtitle("Military Spending") +
  xlab("") +          
  ylab("Relative Share (%)") +
  scale_fill_manual(values = c("#D55E00", "#0072B2"), labels = c("China", "US")) +
  theme_economist_white(gray_bg = FALSE) +
  my_personal_theme

```

3.3: Coercive power in 2021 *(Global Firepower, 2021)*. 

```{r, echo = FALSE, message = FALSE, warning = FALSE, dpi=600}

supperpower_military_power <- tibble(country = c("China", "US"),
                                     aircraft_carriers = c(2, 11),
                                     destroyers = c(50, 92),
                                     submarines = c(79, 68),
                                     fighters = c(1200, 1956)) %>%
  gather(key = measure, value = value, -1)  %>%
  group_by(measure) %>%
  mutate(value = value / sum(value))

supperpower_military_power %>%
  mutate(measure = factor(measure, levels = c("aircraft_carriers", "destroyers", 
                                              "submarines", "fighters"))) %>%
  mutate(country = factor(country, levels = c("China", "US"))) %>%
  ggplot(aes(x = measure, y = value, fill = country)) +
  geom_bar(alpha = 0.9, stat='identity', position="fill") +
  ggtitle("Coercive Power") +
  xlab("") +
  ylab("Relative Share (%)") +
  scale_x_discrete(labels = c("Aircraft Carriers", "Destroyers",
                              "Submarines", "Fighter Jets")) +
  scale_fill_manual(values = c("#D55E00", "#0072B2"), labels = c("China", "US")) +
  theme_economist_white(gray_bg = FALSE) +
  my_personal_theme

```

## **Superpower Summary**
The US appears to depend far less on regional trade, suggesting that its increased military presence may be more an attempt to contain a rising China rather than to secure its economic interests.

While the balance of power currently appears to be in the US's favor, China's much larger population means that this could change quickly if its economy continues to grow in the future. This is especially relevant for the prospect of future conflict, as China would be operating in waters closer to home and thus likely have a strategic advantage. 

&nbsp;

## **Sources**

- Allianz (2016) https://www.agcs.allianz.com/news-and-insights/reports/panama-canal-expansion.html

- CSIS (2016) https://chinapower.csis.org/

- CSIS (2021) https://amti.csis.org/

- EIA (2017) https://www.eia.gov/todayinenergy/detail.php?id=39932

- Global Firepower (2021) https://www.globalfirepower.com/

- Kenawy (2015) http://oaji.net/articles/2017/3667-1488117386.pdf

- Osler (2019) https://lloydslist.maritimeintelligence.informa.com/LL1127721/

- Teh (2019) https://oceans.ubc.ca/research/publications/research-reports/

- World Bank (2019) https://data.worldbank.org/

&nbsp;
&nbsp;
&nbsp;
&nbsp;



